% For copyright and license information, see uiucthesis2021.dtx and derivatives.
\documentclass{uiucthesis2021}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{microtype}
\usepackage{amsmath,amsthm,amssymb}
\usepackage[bookmarksdepth=3,linktoc=all,colorlinks=true,urlcolor=blue,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage[capitalize]{cleveref}
\usepackage[style=ieee, dashed=false]{biblatex}

% Added packages
\usepackage{graphicx}
\usepackage{relsize}
\usepackage{array}
\usepackage{listings}
% \usepackage{caption}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{csvsimple}
\usepackage{longtable}
\usepackage[acronym,toc]{glossaries}

% \usepackage{ruledchapters}  % example of compliant heading format, uncomment to use

\usepackage{lipsum}  % just for placeholder code

% uncomment the below to show a grid on all pages
% \usepackage[grid, gridunit=in, gridcolor=blue!40, subgridcolor=blue!20]{eso-pic}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\addbibresource{./references.bib}

\newcounter{counterforappendices}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{A Reactor Physics Framework to Detect Anomalies in HTGR Core}
\author{Harun Ardiansyah}
\department{Nuclear, Plasma, and Radiological Engineering}
%\concentration{Coffee Studies}
\phdthesis
\degreeyear{2025}
\committee{
    Professor Tomasz Kozlowski, Director of Research, Chair\\
    Professor Angela Di Fulvio\\
    Assistant Professor Syed Bahauddin Alam\\
    Professor Eduard-Wilhelm Kirr\\
    Professor Christophe Demazière}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\frontmatter

\include{acronyms}

\begin{abstract}
This is a comprehensive study of caffeine consumption by graduate
students at the University of Illinois who are in the very final
stages of completing their doctoral degrees. A study group of six
hundred doctoral students\ldots.
\end{abstract}

\begin{dedication}
To my family back home in Indonesia, for their unwavering support and encouragement. To Nafi, the love of my life. To Ali, who makes my life complete.
\end{dedication}

\begin{acknowledgments}

All praises due to Allah, the God Almighty, for guiding me throughout this research endeavor and granting me success along the way. This dissertation is the culmination of many prayers. Most importantly from my family back home in Indonesia. I thank my parents, Mohammad Sholeh and Latifah, for believing in me, for giving me the confidence to move out from our hometown pursue study since I was in high school. I also want to thank my brother, Muhamad Subhan, for allowing me to pursue my study, and always being home during my absences. I would like to thank my wife, Annafiatur Regatra, for always being there for me, for being supportive of my research endeavor and have the confidence in me along my study. For trusting me as a husband, father, and scholar. Finally, I would like to thank my son, Ali Zein Ardiansyah. I will be a while for you to be able to read this dissertation, but your presence complete me. I will do everything in my power for you in the future.

I would like to acknowledge and thank all my teachers, present and the past, for helping me finding my passion in nuclear engineering. Especially, I would like to thank my PhD advisor, Prof. Tomasz Kozlowski, for his confidence in me to pursue neutron noise method as my topic for dissertation. I am thankful for all your encouragement to push me forward towards my study. Prof. Kozlowski also gave me a lot of opportunity for me to grow as a scholar. From writing skills, teaching, mentoring, and being confident in a conference, thank you for your support during my PhD study.

I would like to thank all the professors who served in my committee. Profs. Angela Di Fulvio, Syed Bahauddin Alam, Eduard Wilhelm Kirr, and Christophe Demazière, not only for reviewing my dissertation, but also for giving me meaningful insights along the way. I would like to especially thank Prof. Christophe Demazière for his guidance so far. I still remember my first meeting with Christophe in Gothenburg discussing my initial proposal for this thesis. I did not know a lot about neutron noise back then, but his support and guidance help me to formulate my objectives for this dissertation. Special thanks also to Prof. April Novak. Being Prof. Novak's teaching assistant for the last 3 semesters has helped me with my communication skills with students and how to proactively engage with students.

I would like to also thank NPRE family and staff, for helping me along my study. Coming in to NPRE as "COVID graduates" makes me want to work from home more at the time. But along the way, I learned that being on campus and able to interact with everybody in the department really help me to advance my progress. I would like to appreciate Kristie Stramaski for helping me with all the problems that I got into during my PhD. I would like to also thank Barbara Russell, Sarah Drum, and Becky Meline for helping me during my study at NPRE. Special thanks for all the people at Talbot 223. Thank you Dr. Roberto Agosta, Dr. Alvin Lee, Runxia Wen, Yifan Mao, Silvana Tabares, and all the people whose interaction I really appreciate.

\textit{And finally, I would like to thank YOU, the reader, for considering this out of many literatures out there. I hope this dissertation is professionally meaningful and contributes to everything that you are looking for.}

\end{acknowledgments}

{
    \hypersetup{linkcolor=black}  % disable link coloring locally
    \tableofcontents
    % the Graduate College doesn't recommend including lot or lof
    % \listoftables
    % \listoffigures
}

%\chapter{List of Abbreviations}
%
%\begin{abbrevlist}
%\item[CA] Caffeine Addict.
%\item[CD] Coffee Drinker.
%\end{abbrevlist}
%
%\chapter{List of Symbols}
%
%\begin{symbollist}[0.7in]
%\item[$\tau$] Time taken to drink one cup of coffee.
%\item[$\mu$g] Micrograms (of caffeine, generally).
%\end{symbollist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mainmatter

\chapter{Introduction}
\input{ch1_introduction}

\chapter{Literature Review}
\input{ch2_literature_review}


\chapter{Application Neutron Noise Methods in 2D and 3D HTTR}

\section{Simulation of Neutron Noise in 2D and 3D HTTR}

\section{Application of Neutron Noise Unfolding methods for HTTR}


\chapter{Novel Neutron Noise Unfolding methods and applications}


\chapter{Conclusions}

We conclude that graduate students like coffee.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% per Graduate College preference, place the \appendix and the appendices content before the
% bibliography (here) only if the appendices contain references.
\backmatter

\printbibliography[heading=bibintoc,title={References}]

% the below lines are only needed if bibliography precedes appendices
% uses https://tex.stackexchange.com/a/440212 to continue page numbering
\clearpage
\setcounter{counterforappendices}{\value{page}}
\mainmatter
\setcounter{page}{\value{counterforappendices}}

%\appendix

%\chapter{An appendix}

%\lipsum[1-5]

% \input{Appendix.tex}

\end{document}
