% For copyright and license information, see uiucthesis2021.dtx and derivatives.
\documentclass{uiucthesis2021}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{microtype}
\usepackage{amsmath,amsthm,amssymb}
\usepackage[bookmarksdepth=3,linktoc=all,colorlinks=true,urlcolor=blue,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage[capitalize]{cleveref}
\usepackage[style=ieee]{biblatex}

% Added packages
\usepackage{graphicx}
\usepackage{relsize}
\usepackage{array}
\usepackage{listings}
% \usepackage{caption}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{csvsimple}
\usepackage{longtable}

% \usepackage{ruledchapters}  % example of compliant heading format, uncomment to use

\usepackage{lipsum}  % just for placeholder code

% uncomment the below to show a grid on all pages
% \usepackage[grid, gridunit=in, gridcolor=blue!40, subgridcolor=blue!20]{eso-pic}

\addbibresource{./references.bib}

\newcounter{counterforappendices}

\begin{document}

\title{A Reactor Physics Framework to Detect Anomalies in HTGR Core}
\author{Harun Ardiansyah}
\department{Nuclear, Plasma, and Radiological Engineering}
%\concentration{Coffee Studies}
\phdthesis
\degreeyear{2025}
\committee{
    Professor Tomasz Kozlowski, Director of Research, Chair\\
    Professor Angela Di Fulvio\\
    Assistant Syed Bahauddin Alam\\
    Professor Eduard-Wilhelm Kirr\\
    Professor Christophe Demazière}
\maketitle

\frontmatter

\begin{abstract}
This is a comprehensive study of caffeine consumption by graduate
students at the University of Illinois who are in the very final
stages of completing their doctoral degrees. A study group of six
hundred doctoral students\ldots.
\end{abstract}

\begin{dedication}
To my family back home in Indonesia, for their unwavering support and encouragement. To Nafi, the love of my life. To Ali, who makes my life complete.
\end{dedication}

\begin{acknowledgments}
This dissertation is ...This project would not have been possible without the support of
many people. Many thanks to my adviser, Lawrence T. Strongarm, who
read my numerous revisions and helped make some sense of the
confusion. Also thanks to my committee members, Reginald Bottoms,
Karin Vegas, and Cindy Willy, who offered guidance and support.
Thanks to the University of Illinois Graduate College for awarding
me a Dissertation Completion Fellowship, providing me with the
financial means to complete this project. And finally, thanks to
my husband, parents, and numerous friends who endured this long
process with me, always offering support and love.
\end{acknowledgments}

{
    \hypersetup{linkcolor=black}  % disable link coloring locally
    \tableofcontents
    % the Graduate College doesn't recommend including lot or lof
    % \listoftables
    % \listoffigures
}

%\chapter{List of Abbreviations}
%
%\begin{abbrevlist}
%\item[CA] Caffeine Addict.
%\item[CD] Coffee Drinker.
%\end{abbrevlist}
%
%\chapter{List of Symbols}
%
%\begin{symbollist}[0.7in]
%\item[$\tau$] Time taken to drink one cup of coffee.
%\item[$\mu$g] Micrograms (of caffeine, generally).
%\end{symbollist}

\mainmatter

\chapter{Introduction}
\input{ch1_introduction}

\chapter{Literature Review}
\input{ch2_literature_review}


\chapter{Application Neutron Noise Methods in 2D and 3D HTTR}

\section{Simulation of Neutron Noise in 2D and 3D HTTR}

\section{Application of Neutron Noise Unfolding methods for HTTR}


\chapter{Novel Neutron Noise Unfolding methods and applications}


\chapter{Conclusions}

We conclude that graduate students like coffee.

% per Graduate College preference, place the \appendix and the appendices content before the
% bibliography (here) only if the appendices contain references.

\backmatter

\printbibliography[heading=bibintoc,title={References}]

% the below lines are only needed if bibliography precedes appendices
% uses https://tex.stackexchange.com/a/440212 to continue page numbering
\clearpage
\setcounter{counterforappendices}{\value{page}}
\mainmatter
\setcounter{page}{\value{counterforappendices}}

%\appendix

%\chapter{An appendix}

%\lipsum[1-5]

% \input{Appendix.tex}

\end{document}
